---
name: "Michael J."
surname: "Dark"
given-name-pattern: "M. J."
family-name-pattern: "Dark"
degrees: "D.V.M., Ph.D., Dip. ACVP"
position: "Executive Director, Veterinary Diagnostic Laboratories \\tabularnewline Clinical Associate Professor"
institution: "University of Florida College of Veterinary Medicine"
address: "P.O. Box 100116 \\tabularnewline Gainesville, FL 32610-0116"
phone: +1 352 294 4138
email: "darkmich@ufl.edu"
orcid: "0000-0002-6547-1298"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "005500"
fontsize: "12pt"
csl: mjd-cv.csl # change this if you want to use other citation styles
output: 
  vitae::hyndman:
    pandoc_args: ["--lua-filter=lua/strong.lua"]
header-includes:
  - \DeclareUnicodeCharacter{3B1}{\ensuremath{}}
  - \DeclareUnicodeCharacter{202C}{\ensuremath{}}
  - \newcommand{\mathsemicolon}{\&}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
source("CV_Data.R")
#rmarkdown::pandoc_version()
```

# Education

## Degrees

```{r}
edu %>% 
  detailed_entries(Degree, Year, Where, Institution)
```

## Board Certification

```{r}
boards %>%    
  
  brief_entries(
    Desc,
    Year, 
    Type
  )
```

## Other Training

``` {r}
training %>%
  brief_entries(What, Year, Who)
```

# Employment

```{r}
employment %>% 
  detailed_entries(
    Position,
    Year, 
    Where,
    Institution, .protect=FALSE
  )
```

# Professional Licensure

```{r}
licenses %>%
  detailed_entries(Type, State, Year, LicenseNum)
```  

# Honors and Awards

```{r}
honors %>% 
  brief_entries(
    Type,
    Year, 
    Desc
  )
```

# Publications

```{r}
source("generate_pubs.R")
```

## Journal Articles

```{r results='markup'}
pubs <- bibliography_entries("pubs.bib")
pubs

```

## Book Chapters

```{r}
bibliography_entries("books.bib")
```

# Teaching Experience

## University of Florida - Gainesville, FL
``` {r}
UFteaching %>%   detailed_entries(Class, Course, Year, Position, Info)
```

## Washington State Unversity - Pullman, WA
``` {r}
WSUteaching %>%   detailed_entries(Class, Course, Year, Position, Info)
```

# Graduate Students

```{r}
grad_students %>% detailed_entries(Student, Position, Year, Department, Info)
```

# Presentations and Invited Lectures

## Presentations

``` {r}
presentations %>% detailed_entries(Title, When, Where, Who, What)
```

## Invited Lectures

```{r}
invited_lectures %>% detailed_entries(Title, When, Where, Who, What)
```

# University Service

``` {r}
university_service %>%
  detailed_entries(What, When)

```


<!-- This is how to keep things on one page - first is ending block, second is starting block -->
<!-- ```{=latex} -->
<!-- \end{minipage} -->
<!-- ``` -->

<!-- ```{=latex} -->
<!-- \begin{minipage}{\textwidth} -->
<!-- ``` -->


# Grants

```{r}
grants %>% detailed_entries(Position, When, PI, Title, Info)
```

# Professional Service

## Professional Organizations

```{r}
orgs %>% detailed_entries(Position, When, PI, Title, Info)
```

## Ad-hoc Peer Review:

```{r ad-hoc, results="markup"}
pander::pander(adhoc, keep.line.breaks = T, style = 'grid', justify = 'left', caption=NULL)
   
```

## Ad-hoc Grant Reviews

* US / Israel Binational Agricultural Research and Development Fund 
* Horserace Betting Levy Board Veterinary Advisory Committee (UK)

## External Promotion Reviewer
* Washington State University
* University of California at Davis
